CO Interlopers Eloping from [C~\textsc{ii}] Surveys

### 2019-03-24 paper/ms.tex
Add Fisher matrix intro
Add high precision regime

>>>>

The Fisher matrix for our measurement is
\beq\label{eq:fisher}
F_{i,j} = 
\int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\sum_{\substack{l,l'\\l > l'}} \sum_{\substack{m,m'\\m > m'}}
\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\text{,}
\eeq
where $l$, $l'$, $m$, and $m'$ sum over all lines being considered. Note that
we can make the substitution
\begin{equation*}
\sum_{\substack{l,l'\\l > l'}} \rightarrow 
\frac{1}{2} \sum_{\substack{l,l'\\l \neq l'}}\text{,}
\end{equation*}
without changing the value of the Fisher matrix. Thus it will be easier to compute
\beq\label{eq:fisher4}
F_{i,j} = 
\frac{1}{4} \int \frac{\text{d}k\,k^2}{2\pi^2} V_{\text{surv}} 
\sum_{\substack{l,l'\\l \neq l'}} \sum_{\substack{m,m'\\m \neq m'}}
\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\text{,}
\eeq

\subsection{High Precision Regime}\label{ssec:high_precision}
To build some intuition, we consider the idealized case with no interloper,
foreground, or detector noise. This is achievable in principle, though
certainly not with current techniques and instruments. In this case, we have
that $\pstot{i} = \xps{i}{i}$. Therefore, we can modify the variance and
covariance formulas from before as
\beq
\begin{split}
\Var{\xps{i}{j}} &= 2(B_iB_j)^2 \denps(k)^2 \\
\Cov{\xps{i}{j}}{\xps{i}{k}} &= 2B_i^2B_jB_k\denps(k)^2\text{.}
\end{split}
\eeq
We are now in a position to write down a general formula for the covariance
between two cross-spectra,
\beq\label{eq:cov_kron}
\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} =
\frac{1}{2B_l B_{l'} B_m B_{m'}}
\left(\delta_{lm} + \delta_{lm'} + \delta_{l'm} + \delta_{l'm'} -
\delta_{lm}\delta_{l'm'} - \delta_{lm'}\delta_{l'm}\right)
\frac{1}{\denps(k)^2}\text{,}
\eeq
where the $\delta_{lm}$ is the Kronecker delta, and same for $\delta_{l'm}$,
etc. We can also similarly write down a formula for the power spectrum
derivative as
\beq\label{eq:ps_deriv}
\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}
= \left( B_l \delta_{il'} + B_{l'}\delta_{il} \right) \denps(k)\text{.}
\eeq
Combining the two results gives
\beq\label{eq:cov_and_deriv}
\begin{split}
\frac{\partial \hat{P}_{l,l'}(k)}{\partial B_i}&
\frac{1}{\Cov{\hat{P}_{l,l'}(k)}{\hat{P}_{m,m'}(k)}} 
\frac{\partial \hat{P}_{m,m'}(k)}{\partial B_j}\\ 
&= 
\frac{(B_l \delta_{il'} + B_{l'} \delta_{il})(B_m \delta_{jm'} + B_{m'} \delta_{jm})}
{2 B_l B_{l'} B_m B_{m'}}
\left(\delta_{lm} + \delta_{lm'} + \delta_{l'm} + \delta_{l'm'}
-\delta_{lm}\delta_{l'm'} - \delta_{lm'}\delta_{l'm}\right)\text{.}
\end{split}
\eeq
Note that this product is independent of $k$. As a result, we can pull it out of the integral in Equation~\ref{eq:fisher4}. We can then perform that integral. If we then define
\begin{equation*}
\tilde{V}_k \equiv \frac{k_{\text{max}}^3}{6\pi^2} V_{\text{surv}}\text{,}
\end{equation*}
then we can write the Fisher matrix as
\beq
F_{i,j} = \frac{\tilde{V}_k}{4}
\sum_{\substack{l,l'\\l \neq l'}} \sum_{\substack{m,m'\\m \neq m'}}
\frac{(B_l \delta_{il'} + B_{l'} \delta_{il})(B_m \delta_{jm'} + B_{m'} \delta_{jm})}
{2 B_l B_{l'} B_m B_{m'}}
\left(\delta_{lm} + \delta_{lm'} + \delta_{l'm} + \delta_{l'm'}
-\delta_{lm}\delta_{l'm'} - \delta_{lm'}\delta_{l'm}\right)\text{.}
\eeq

Since the factor that comes before the $(\delta_{lm} + \delta_{lm'} +
\delta_{l'm} + \delta_{l'm'})$ term is symmetric under $l\rightarrow l'$ and
$m\rightarrow m'$, we can replace it by $4\delta_{lm}$. One can show by direct
computation that the $\delta_{lm}\delta_{l'm'}$ and $\delta_{lm'}\delta_{l'm}$
terms vanish, and so we can write
\beq
F_{i,j} = \tilde{V}_k
\sum_{\substack{l,l'\\l \neq l'}} \sum_{\substack{m,m'\\m \neq m'}}
\frac{(B_l \delta_{il'} + B_{l'} \delta_{il})(B_m \delta_{jm'} + B_{m'} \delta_{jm})}
{2 B_l B_{l'} B_m B_{m'}}
\delta_{lm}\text{.}
\eeq
It is then possible to show that
\beq\label{eq:fisher_perfect}
    F_{i,j}=\frac{\tilde{V}_k}{2B_iB_j} \times
    \begin{cases}
         N(N-1) & \text{if $i=j$} \\
         3N-4 &\text{if $i\neq j$} \\
    \end{cases}
\eeq
where $N$ is the number of lines being considered. This can be inverted by
guessing a functional form after working out a few test cases to give
\beq\label{eq:cov_perfect}
    C_{i,j} = (F^{-1})_{i,j}=\frac{B_iB_j}{2\tilde{V}_k\left[(N-2)(N-1)\right]^2} \times
    \begin{cases}
         4N^2 - 11N + 8 & \text{if $i=j$} \\
         4-3N &\text{if $i\neq j$} \\
    \end{cases}
\eeq
Note that the diagonal elements scale like $1/N^2$ while the off-diagonal
elements scale like $1/N^3$. What this means is that in the large $N$ limit,
the covariance matrix approaches diagonality. In particular, we can write that
\beq\label{eq:cov_perfect_largeN}
C_{i,j} \rightarrow \frac{2B_i^2}{N^2 \tilde{V}_k} \delta_{ij}\text{.}
\eeq
Note that this is equivalent to a perfect auto-spectrum measurement of volume
$N^2 V_{\text{surv}}$. Therefore, with $N$ measurements of a volume
$V_{\text{surv}}$, one can have the constraining power of a volume $N^2
V_{\text{surv}}$!
